### 2022-08-24 manuscript.Rmd
Small fixes

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE,
  control_analysis = TRUE,
)

@@

```{r, figclusters, include=TRUE, fig.height=8}
# Read results of cluster-based permutation tests for ERPs
read_csv(here(output_dir, "clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> clusters

# Plot thresholded cluster images
clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  theme(legend.position = "top")
```

```{r, figtfrclusters, fig.height=12, include=TRUE}
# Read results of cluster-based permutation tests for TFR
read_csv(here(output_dir, "tfr_clusters.csv"), col_types = cols(
  contrast = col_factor(levels = c(
    "Pre-insight/Informed - Pre-insight/Naive",
    "Insight/Informed - Insight/Naive",
    "Post-insight/Informed - Post-insight/Naive"
  ))
)) -> tfr_clusters

# Plot thresholded cluster images for the insight phase
tfr_clusters %>%
  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")

# Plot thresholded cluster images for the post-insight phase
tfr_clusters %>%
  filter(
    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
  ) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")
```

>>>>

# Re-run steps that take a long time to compute?
run <- list(
  eeg_processing = TRUE,
  mixed_models = TRUE,
  control_analysis = TRUE
)

@@

```{r, figclusters, include=TRUE, fig.height=8}
# Plot thresholded cluster images
clusters %>%
  filter(p_val < .05) %>%
  ggplot(aes(x = time, y = channel, fill = cluster)) +
  facet_grid(~contrast, drop = FALSE) +
  geom_raster() +
  theme(legend.position = "top")
```

```{r, figtfrclusters, fig.height=12, include=TRUE}
# Plot thresholded cluster images for the insight phase
tfr_clusters %>%
  filter(contrast == "Insight/Informed - Insight/Naive" & p_val < .05) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")

# Plot thresholded cluster images for the post-insight phase
tfr_clusters %>%
  filter(
    contrast == "Post-insight/Informed - Post-insight/Naive" & p_val < .05
  ) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")

# Plot thresholded cluster images for the control analysis
tfr_clusters %>%
  filter(
    contrast == "Insight/Informed - Insight/Exclude_informed" & p_val < .05
  ) %>%
  ggplot(aes(x = time, y = freq, fill = cluster)) +
  facet_wrap(~channel) +
  geom_raster() +
  theme(legend.position = "top")
```
